---
title: "Usage with JSON: Remote Example"
output: rmarkdown::html_vignette
package: vitessce
vignette: >
  %\VignetteIndexEntry{Usage with JSON: Remote Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(
  root.dir = dirname(dirname(getwd())),
  rmarkdown.pandoc.to = knitr::opts_knit$get("rmarkdown.pandoc.to")
)
```

The following is an example of usage of the widget with JSON files. In this example, the JSON files are stored on a remote AWS S3 bucket. For information about remote file hosting, please visit the [Hosting Data](http://vitessce.io/docs/data-hosting/) page of the main Vitessce documentation website.

## Configure the Vitessce widget

Add JSON files to the dataset using the `add_file` function. The `add_file` function returns the updated dataset, allowing the function calls to be chained.

```{r echo = TRUE, warning = FALSE}
library(vitessceR)

base_url <- "https://s3.amazonaws.com/vitessce-data/0.0.31/master_release/linnarsson/"

# Create Vitessce view config
vc <- VitessceConfig$new("Codeluppi et al., Nature Methods 2018")
dataset <- vc$add_dataset("Codeluppi")$add_file(
  url = paste0(base_url, "linnarsson.cells.json"),
  data_type = DataType$CELLS,
  file_type = FileType$CELLS_JSON
)$add_file(
  url = paste0(base_url, "linnarsson.cell-sets.json"),
  data_type = DataType$CELL_SETS,
  file_type = FileType$CELL_SETS_JSON
)$add_file(
  url = paste0(base_url, "linnarsson.molecules.json"),
  data_type = DataType$MOLECULES,
  file_type = FileType$MOLECULES_JSON
)$add_file(
  url = paste0(base_url, "linnarsson.clusters.json"),
  data_type = DataType$EXPRESSION_MATRIX,
  file_type = FileType$CLUSTERS_JSON
)$add_file(
  url = paste0(base_url, "linnarsson.raster.json"),
  data_type = DataType$RASTER,
  file_type = FileType$RASTER_JSON
)

desc <- vc$add_view(dataset, Component$DESCRIPTION)
desc <- desc$set_props(description = "Codeluppi et al., Nature Methods 2018: Spatial organization of the somatosensory cortex revealed by osmFISH.")

spatial <- vc$add_view(dataset, Component$SPATIAL)
spatial_layers <- vc$add_view(dataset, Component$LAYER_CONTROLLER)

scatterplot_pca <- vc$add_view(dataset, Component$SCATTERPLOT, mapping = "PCA")
scatterplot_tsne <- vc$add_view(dataset, Component$SCATTERPLOT, mapping = "t-SNE")
status <- vc$add_view(dataset, Component$STATUS)

cell_sets <- vc$add_view(dataset, Component$CELL_SETS)
gene_list <- vc$add_view(dataset, Component$GENES)
heatmap <- vc$add_view(dataset, Component$HEATMAP)$set_props(transpose = TRUE)

vc$layout(hconcat(
  vconcat(vconcat(desc, status), spatial_layers),
  vconcat(heatmap, spatial),
  vconcat(scatterplot_tsne, scatterplot_pca),
  vconcat(gene_list, cell_sets)
))
```

```{r eval = FALSE, echo = TRUE}
# Render the Vitessce widget
vc$widget(theme = "light", width = "100%")
```

```{r eval = TRUE, echo = FALSE}
if(!is.null(knitr::opts_knit$get("rmarkdown.pandoc.to")) && knitr::opts_knit$get("rmarkdown.pandoc.to") == "html") {
  vc$widget(theme = "light", width = "100%")
}
```



